### 2023-02-07 chapter3/chapter3.tex
Added abstract for chapter3

\begin{abstract}
\noindent
Abstract text for this chapter
\end{abstract}

>>>>

\begin{abstract}
\noindent
Fitting statistical models to data is often a key step in the scientific method because it can formalize hypotheses and conclusions as unambiguous and testable statements. The major scientific computing library for the programming language Python, SciPy, provides ready-to-use implementations of core statistical functions, which allows users with varying levels of expertise to easily apply them to their data. However, SciPy does not support two common and powerful types of models called mixture models and hidden Markov models (HMMs). Other more specialized packages such as hmm-learn and pomegranate provide implementations for a restricted subset of these models, but they use APIs which are not compatible with SciPy. This can pose a barrier to entry for beginners and prevent more advanced users from easily extending these packages' capabilities. We therefore created two packages, MixMod and Homomorph, that implement mixture models and HMMs, respectively, and conform to the SciPy API for specifying distributions. Each package is fully documented, and we wrote a set of tutorials which both introduce their APIs and illustrate various training techniques through a series of examples. These packages are available on the Python Package Index (PyPI) under the names mixmod and homomorph, and the source code is hosted alongside the tutorials on GitHub at \url{https://github.com/marcsingleton/mixmod} and \url{https://github.com/marcsingleton/homomorph}, respectively.
\end{abstract}
